Binary companions of red giant stars in \apogee\ \DR: \\ Search method and catalog of $>$4,500 systems

### 2018-03-08 paper/1-catalog/twoface-catalog.tex
bimodal table

\begin{table}
    \centering
    \begin{tabular}{c | c | c | c}
    \texttt{APOGEE\_ID} & \texttt{P} & \texttt{e} & \texttt{K} \\
    & $\mathrm{d}$ & & $\mathrm{km\,s^{-1}}$ \\
    \hline
    2M21362657-0017579 & 14.639 & 0.1171 & 30.68 \\
    2M21362657-0017579 & 2.3049 & 0.0026 & 28.69 \\
    2M03180303-0004215 & 35.553 & 0.1302 & 4.541 \\
    2M03180303-0004215 & 107.22 & 0.3192 & 8.792 \\
    ... & ... & ...
    \end{tabular}
    \caption{This table contains \texttt{APOGEE\_ID}'s and limited orbital
    parameter information for all \nbimodal\ stars identified as having bimodal
    posterior samplings in orbital period.
    Each source is listed twice, with MAP values of period, \texttt{P},
    eccentricity, \texttt{e}, and velocity semi-amplitude, \texttt{K}, from each
    period mode of the posterior sampling for the source.
    }
    \label{tbl:highK-bimodal}
\end{table}

@@

% TODO:
% Notebook: "Results"
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\textwidth]{infer-jitter}
% \end{center}
% \caption{%
% Inferred prior over excess variance parameter ($y = \ln s^2$) using posterior
% samples for 1,825 lower-RGB stars with $>10$ visits.
% Left and right panels show the distribution corresponding to the
% maximum-likelihood parameters $(\mu_y, \sigma_y) = (9.50, 1.64)$ in log and
% linear, respectively.
% \label{fig:infer-jitter}
% }
% \end{figure}

\subsection{Red clump stars lack short-period companions}

\todo{Period-logg plot - lack of short-period companions for red clump stars?}

\todo{also look at trends with Teff?}

\todo{Cite troup, who also noted this}

Red clump (\RC) stars are horizontal branch stars and have therefore already
climbed the RGB, where the surface of the star can grow to be several AU in
size.
\RC\ stars are therefore expected to less frequently have companions at short
periods ($P<XX$~day) because short period companions would have been
common-envelope during the RGB phase.
\figurename~\ref{fig:todo} hints that there is an apparent dearth of
short-period companions around $\log g \sim 2.5$ (the approximate location of
the red clump).
Another way to look at this is to compare the fraction of subgiant stars with
short-period companions to the same for stars near the \RC.

\todo{To assess this, take boxes in log g-Teff}
We find that, empirically, XX\% of the subgiants and YY\% of the \RC\ stars have
companions with $XX < P < XX$~day.
\todo{Assuming selection function doesn't preferentially bias...}

\subsection{Evidence for tidal circularization at $P\sim 10~\textrm{day}$}

>>>>

\begin{table}
    \centering
    \begin{tabular}{c | c | c | c | c | c | c}
    \texttt{APOGEE\_ID} & \texttt{P} & \texttt{e} & \texttt{K} &
        \texttt{M1} & \texttt{M2\_min} & \texttt{clean\_flag} \\
    & $\mathrm{d}$ & & $\mathrm{km\,s^{-1}}$ &
        $\mathrm{M_{\odot}}$ & $\mathrm{M_{\odot}}$ &  \\
    \hline
    2M21362657-0017579 & 14.639 & 0.1171 & 30.68 & -- & -- & 0 \\
    2M21362657-0017579 & 2.3049 & 0.0026 & 28.69 & -- & -- & 0 \\
    2M03180303-0004215 & 35.553 & 0.1302 & 4.541 & 1.20 & 0.20 & 0 \\
    2M03180303-0004215 & 107.22 & 0.3192 & 8.792 & 1.20 & 0.13 & 0 \\
    ... & ... & ... \\
    \multicolumn{6}{c}{\textit{(210 rows)}}
    \end{tabular}
    \caption{This table contains \texttt{APOGEE\_ID}'s and limited orbital
    parameter information for all \nbimodal\ stars identified as having bimodal
    posterior samplings in orbital period.
    Each source is listed twice, with MAP values of period, \texttt{P},
    eccentricity, \texttt{e}, and velocity semi-amplitude, \texttt{K}, from each
    period mode of the posterior sampling for the source.
    When available, this table also includes point-mass estimates of the primary
    mass, \texttt{M1}, from \citet{Ness:2015}, and minimum companion masses,
    \texttt{M2\_min}, computed for each period mode.
    }
    \label{tbl:highK-bimodal}
\end{table}

@@

% Notebook: "Results"
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.7\textwidth]{mass}
\end{center}
\caption{%
TODO
\label{fig:mass}
}
\end{figure}

\subsection{Evidence for tidal circularization}
